The \raveon\ catalog of stellar atmospheric parameters and\\ chemical abundances for chemo-dynamic studies in the \gaia\ era

### 2017-03-14 referee-response-scientific-v1.txt

    We have included the figure requested by the referee, and added a paragraph
    to the text that references this figure in the appropriate section of the
    manuscript:

        The weighted labels for all stars are shown as normalized historgrams in
        Figure \ref{fig:label-histograms}. The normalization in each axis is arbitrary, 
        since main-sequence stars do not have detailed abundances here, there are fewer
        stars with -- for example, [Ni/H] labels -- than there are stars with $\teff$
        labels. The [X/H] abundance distributions peak near Solar values, and the peaks
        in the $\teff$ and $\logg$ histograms are consistent with our expectations from
        astrophysics: the build of clump stars is visible for cool giant stars 
        ($\logg \approx 2.5$ and $\teff \approx 4750$~K), and the increase in turn-off stars
        at $\teff \approx 6000$~K is expected given the longer timescales for the turnoff.

    Unfortunately the earliest that we could reasonably include this Figure is 
    in Section 3.6 (making this new figure, Figure 6) without disturbing the
    explanatory flow of the paper.

    We have also included an additional paragraph that outlines how our assumption of 
    pixel independence is violated, and the (negligible) impact that has on our results.
    The added text reads:

	One of these assumptions is that the noise in individual pixels is independent
	(between adjacent pixels). The description of the data reduction in the fifth 
	\rave\ data release paper \citep{Kunder_2016} shows that this assumption is
	incorrect.  The noise in neighbouring pixels is correlated in two ways: first
	due to the oversampling by the CCD pixels in the spectrograph's point spread
	function, and due to a 3-pixel boxcar smoothing that was later applied
	to the data.  While it is unlikely that our assumption of pixel independence
	violates any of our results, it explains in part why our original errors were
	underestimated.  However, there are other assumptions made that potentially
	have more serious consequences on the validity or utility of our results.

### 2017-03-14 referee-response-statistical-v1.txt

-- Author's response:

    The referee is correct. We did not consider Bayesian Model Averaging here in
    part due to computational cost. We have added some text to Section 5 which
    remarks on this:

        Because the relative weights have no formal interpretation, it is reasonable
        to consider this method is as \emph{ad hoc} as any other approach.  The relative 
        weighting has no warranty to be (formally) correct, and therefore may introduce 
        inconsistencies or systematic errors rather than minimizing them.  While Bayesian
        model averaging \citep[e.g., ][and similar methods]{Hoeting_1999} repreresent more
        formal and considered approaches to weighting -- or deciding between -- multiple 
        models, these approaches were not considered here due in part to their higher 
        computational cost.

-- Author's note:

    We note that we have included an additional paragraph that outlines how our assumption of pixel independence is violated, and the (negligible) impact that has on our results. The added text reads:

	One of these assumptions is that the noise in individual pixels is independent
	(between adjacent pixels). The description of the data reduction in the fifth 
	\rave\ data release paper \citep{Kunder_2016} shows that this assumption is
	incorrect.  The noise in neighbouring pixels is correlated in two ways: first
	due to the oversampling by the CCD pixels in the spectrograph's point spread
	function, and due to a 3-pixel boxcar smoothing that was later applied
	to the data.  While it is unlikely that our assumption of pixel independence
	violates any of our results, it explains in part why our original errors were
	underestimated.  However, there are other assumptions made that potentially
	have more serious consequences on the validity or utility of our results.

### 2017-03-14 article/unrave.tex
Address pixel correlations. Closes #35

>>>>

One of these assumptions is that the noise in individual pixels is independent
(between adjacent pixels). The description of the data reduction in the fifth 
\rave\ data release paper \citep{Kunder_2016} shows that this assumption is
incorrect.  The noise in neighbouring pixels is correlated in two ways: first
due to the oversampling by the CCD pixels in the spectrograph's point spread
function, and due to a 3-pixel boxcar smoothing that was later applied
to the data.  While it is unlikely that our assumption of pixel independence
violates any of our results, it explains in part why our original errors were
underestimated.  However, there are other assumptions made that potentially
have more serious consequences on the validity or utility of our results.
